% \documentclass[12pt,legalpaper]{article}
% % \documentclass[12pt]{report}
% \usepackage[a4paper, total={6in, 8in}]{geometry}
% \large
% \usepackage{booktabs}
% \usepackage{setspace}
% % \usepackage{hyperref}
% \usepackage[hidelinks]{hyperref}
% \usepackage{graphicx}
% \usepackage{float}
% \usepackage{xcolor}
% \documentclass[12pt]{article}
% % \documentclass[12pt]{report}
% \usepackage[a4paper, total={6in, 8in}]{geometry}
% \large
% \usepackage{booktabs}
% \usepackage{setspace}
% \usepackage{hyperref}
% \usepackage{graphicx}
% \usepackage{float}
% \usepackage{xcolor}
% \usepackage{lscape}

% \begin{document}
\thispagestyle{empty} % no page number for title page
\doublespacing

\section*{\centering Abstract}


This dissertation utilizes empirical and experimental approaches to investigate the multifaceted factors that affect decision-making in economic contexts. The three chapters place a particular focus on group affiliation, perceived discrimination, and the gender gap in entrepreneurship.

The first chapter explores the impact of team diversity on economic decision-making within a dynamic context. Through a series of laboratory experiments involving participants randomly assigned to teams, the study examines how team diversity influences individual behavior and performance. Results indicate that team diversity significantly affects individual behavior, with newcomers being particularly influenced by the diversity of the team they join. The findings underscore the importance of understanding the effects of team composition on decision-making processes and performance outcomes. 

The second chapter delves into the implications of subjective evaluation systems for both supervisors and employees. Through experiments conducted with participants from two U.S. universities, the research examines how group affiliation influences perceived discrimination in economic decision-making. By uncovering disparities in anticipation of bias based on race and gender, the study highlights the importance of addressing systemic biases and fostering inclusive workplace environments.


The third chapter investigates the dynamics of fundraising in early stage startups. Despite dominance in certain female-dominated industries, women entrepreneurs struggle to secure funding. The analysis suggests potential industry-based sorting bias, with women-led ventures performing on par or better in high-funding industries.

Overall, these chapters deepen our understanding of team dynamics, job evaluations, and discrimination perceptions, while also offering insights for creating more inclusive work environments.

\thispagestyle{empty} % no page number for title page
\clearpage


\section*{\centering Acknowledgments}
I thank my Ph.D. Committee, Dr. Sherry Li, Dr. Peter J. McGee, Dr. Andy Brownback, and Dr. Md Amzad Hossain. I am grateful for their guidance and immense support. My main supervisor, Dr. Sherry Li, provided thoughtful advice, challenged my research rigor, and trained me to become an independent researcher. Dr. Peter J. McGee as the PhD program advisor and a committee member offered constructive comments on my research ideas. Dr. Andy Brownback read my draft papers with patience and provided illuminating feedback. I am also grateful to Dr. Md Amzad Hossain for his guidance on navigating the dissertation and the job market.  I am grateful for having the four of them as my mentors and thank their thoughtful training and genuine support.
 
I appreciate the mentoring I received from the Faculty of Economics at Sam M. Walton College of Business, the AEA Mentoring Program and Dr. Manisha Shah of UCLA. 

My Ph.D. program was sponsored the University of Arkansas. I would like to thank the University the generous financial support and for facilitating an enriching academic experience. 

Many people inspired me in this journey. My family's patience with my frequent disconnections due to the tremendous demanding nature of my Ph.D. program was instrumental. My PhD cohort mates Miguel Cuellar, Eric Neyou and Allan "Braziel" Hatch for all the fun times and struggles together.  



\thispagestyle{empty} % no page number for title page
\clearpage



\section*{\centering \textbf{Dedication}}

I dedicate this work to my beloved family. Firstly, to my mother, Comfort Asele, whose brilliant mind, though constrained by a lack of formal education, continuously inspired me to excel in every circumstance. Secondly, to my father, Stephen Atanga Agyeah, for his unwavering financial, emotional, and all-around support. I extend this dedication to my dear siblings, Janet Agyeah and Stephen Agyeah. The times and struggles we have been through together help me to stay rooted and resilient in all situations. Lastly and more significantly, to my daughter, Thelma Talata Agyeah, my cherished wife, Uzoma Vivian Igwe, and my second child, who serve as my enduring motivation to strive for excellence.


% Chapter 1: The National Science Foundation, the University of Arkansas and Behavioral Business Research Lab under the leadership of Dr. Sherry Li. I also extend my gratitude to my research assistants Vera Adabrah, Kaitlyn Pearson and Aashvi Dahiya for their hard work. 


% Chapter 2: Dr. Yufei Ren secured funding for part of this project.  

% Chapter 3: I am grateful to TechCrunch (now Crunchbase) for allowing me to use their data. 
% \thispagestyle{empty} % no page number for title page
% \clearpage
% % \doublespacing
% \thispagestyle{empty} % no page number for title page
% \tableofcontents
% % \clearpage

% \input{Introduction}
% \clearpage

% \part{ Racial and Gender Diversity, Newcomers and Team Performance in a Dynamic Setting}
% \input{Chapter 1}
% \clearpage

% \part{Group bias, anticipation and performance}
% \input{Chapter 2} 
% \clearpage

% \part{Do investors show team composition preferences in funding Startup teams? An analysis of Venture Funding}
% \input{Chapter 3} 
% \clearpage

% \input{Conclusion}
% \clearpage

% \end{document}